Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-01-14 paper/1_Initial/manuscript.qmd
remove weird characters

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Magdalena Pfaff
    orcid: 0009-0006-2386-7936
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
      :::
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| label: "fig-measures"
#| fig-cap: "Different ways in which interoception can be measured."

@@

For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper**]. 
The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures]. 
Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.

@@

```{r}
#| warning: false
#| label: tbl-samples
#| tbl-cap: "Samples demographics"
#| apa-note: "Some note bedlow the table"

knitr::include_graphics("figures/table1.png")

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Magdalena Pfaff
    orcid: 0009-0006-2386-7936
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
      :::
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: jou
  apaquarto-docx: default
  apaquarto-html: default
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| label: "fig-measures"
#| fig-cap: "Different ways in which interoception can be measured."
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

@@

For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper OF MURPHY with the chinese**]. 
The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures]. 
Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.

@@

```{r}
#| label: tbl-samples
#| tbl-cap: "Samples demographics"
#| apa-note: "Some note below the table"

knitr::include_graphics("figures/table1.png")
```
